Towards Language Model-based Identification of Market Segments and Fostering of Business Clusters

### 2023-06-30 report/report.tex
added matriculation number
add paper template

\author{\IEEEauthorblockN{1\textsuperscript{th} Müller Nicola}
\IEEEauthorblockA{s8namuel@stud.uni-saarland.de \\ 2578753}
\and
\IEEEauthorblockN{2\textsuperscript{st} Leist Robert}
\IEEEauthorblockA{s8roleis@stud.uni-saarland.de \\ 2580448}
\and
\IEEEauthorblockN{3\textsuperscript{nd} Eichler Paul}
\IEEEauthorblockA{s8pleich@stud.uni-saarland.de \\ 2578569}
\and
\IEEEauthorblockN{4\textsuperscript{rd} Recktenwald Tobias}
\IEEEauthorblockA{s8tsreck@stud.uni-saarland.de \\ 2577468}
\and
\IEEEauthorblockN{5\textsuperscript{th} Nazari Hameed}
\IEEEauthorblockA{Email Address \\ Matriculation No.}
}

@@

\section{Introduction}
Identifying market segments in regional economies is crucial for effective marketing strategies and making well-informed business decisions. Further, combining geographical data of companies' locations with information on their corresponding market segments allows for detecting business clusters, which are local concentrations of businesses, manufacturers, suppliers, and institutions from the same field. This geographic proximity of related businesses enables efficient cooperation and knowledge transfer, which has been shown to significantly increase the productivity of all businesses within the cluster (citation). Thus, establishing or further developing business clusters is of high interest to companies and local governments.

@@

This work demonstrates how to identify market segments and develop business clusters by introducing an automatic clustering pipeline and location recommendation system for economic data from the German federal state Saarland. The novelty of our approach is that we rely on language models to encode the companies' information.

@@

@@

>>>>

\author{\IEEEauthorblockN{1\textsuperscript{th} Müller Nicola}
\IEEEauthorblockA{s8namuel@stud.uni-saarland.de \\ 2578753}
\and
\IEEEauthorblockN{2\textsuperscript{st} Leist Robert}
\IEEEauthorblockA{s8roleis@stud.uni-saarland.de \\ 2580448}
\and
\IEEEauthorblockN{3\textsuperscript{nd} Eichler Paul}
\IEEEauthorblockA{s8pleich@stud.uni-saarland.de \\ 2578569}
\and
\IEEEauthorblockN{4\textsuperscript{rd} Recktenwald Tobias}
\IEEEauthorblockA{s8tsreck@stud.uni-saarland.de \\ 2577468}
\and
\IEEEauthorblockN{5\textsuperscript{th} Nazari Hameed}
\IEEEauthorblockA{abna00001@stud.uni-saarland.de \\ 7004543}
}

@@

\section{Introduction}

Identifying market segments in regional economies is crucial for effective marketing strategies and making well-informed business decisions. Further, combining geographical data of companies' locations with information on their corresponding market segments allows for detecting business clusters, which are local concentrations of businesses, manufacturers, suppliers, and institutions from the same field. This geographic proximity of related businesses enables efficient cooperation and knowledge transfer, which has been shown to significantly increase the productivity of all businesses within the cluster (citation). Thus, establishing or further developing business clusters is of high interest to companies and local governments.

@@

At the same time, recent advances in natural language processing (NLP), e.g. in the form of the popular ChatGPT \cite{chatgpt}, have led to surprisingly good results in numerous applications. Examples range from complex Code generation to essays to cooking recipes.

This work demonstrates market segments and business clusters can be identified effectively by introducing an automatic clustering pipeline. Utilizing those clusters, our system is then able to provide a strategic location, which we will demonstrate by using the German federal state Saarland as an example. The novelty of our approach is that we rely on language models to encode the companies' information.

@@

\subsection{Identification and Impacts of Business Clusters}

\subsection{Natural Language Processing}

@@

\pe{Maybe we should bring out the connection to our approach here a little bit more}
